---
title: "PG-3 Test Buritos Review Data"
author: "Rishabh"
date: "November 16, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Create a variable called ritos and store your data in it.
```{r}
ritos <- read.csv("Burritos_Data.csv")

```

2. Print the first 6 rows of ritos
```{r}
ritos[1:6,]

```

3. Print the dimension of ritos
```{r}
dim(ritos)

```

4. Filter the data using variable nonSD == 0, store it in ritos and print the dimension of this dataset
```{r}
library(dplyr)
ritos <- filter(ritos, NonSD == 0)
dim(ritos)

```

5. Print the number of unique values for Burito variable
```{r}
unique(ritos$Burrito)

```

6. Using the Burito variable, filter data for california and print the number of unique values for the same. Hint : Use grepl to filter 'california'
```{r}
a<-filter(ritos, grepl('california', ritos$Burrito)) 
length(unique(a$Burrito))

```

7. Select the variables Location and Yelp and print the first 6 rows
```{r}
b <- ritos[c(1,6)]
b[1:6,]

```

8. Select columns with Burito ratings i.e. from Tortilla to Wrap and print the first 6 rows
```{r}
c <- select(ritos, Tortilla:Wrap)   
c[1:6,]
```

9. Create a new data frame df from ritos, select only columns 'Taste', 'Rec',
'Cost', 'Volume
```{r}
df <- select(ritos,Taste,Rec,Cost,Volume) 
```

10. Create a new column('Cost_vol') in the same dataframe df using the formula(Cost/Volume), print the first 6 rows of the df
```{r}
Cost_vol <- ritos$Cost/ritos$Volume
d <- cbind(Cost_vol,df)
d[1:6,]
```

11. Plot(dotplot) Taste on y axis and Cost_vol on x axis for df and colour code by variable Rec
```{r}
library(ggplot2)
ggplot(df, aes(x = Cost_vol, y = Taste))+ 
  geom_point(aes(colour = Rec))
```

12. Select burrito rating variable and recommendation(select variable rec and Tortilla to Taste), store this in a new variable called ing and print the first 6 rows
```{r}
library(data.table)
ing <- select(ritos,c(Rec,Tortilla:Taste))
head(ing)
```

13. Convert the above data to long format and store in variable df.melt; use 'Rec' and 'Taste' as your id variables, print the structure of this dataset
```{r}
#library(UsingR)
library(reshape2)
df.melt<-melt(ing, id.vars=c('Rec','Taste'))
str(df.melt)

```

14. Plot(ggplot and geom_point) the above dataset using x variable 'Taste' and y variable 'Value'
```{r}
ggplot(df.melt, aes(x = Taste, y = value)) + geom_point()

```

15. Create a facet_wrap of df.melt use x-axis="Taste", y-axis="Value" and colour = "variable", use geom_point, add a smoother(lm) using geom_smooth, colour the smoother in "black", give the x axis label as 'Burrito Qulaity' and y-axis label as 'score'
```{r}
ggplot(df.melt, aes(x = Taste, y = value, colour = variable)) +
  geom_point() + geom_smooth(method='lm', color='black') + facet_wrap(~variable) +
  labs(x='Burrito Quality', y='Score')

```
